Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-01-22 writeup/gz_hubble_data.tex

@@

@@

Needs: coordinate/location description.

So GZ:CANDELS overlaps with GZ:Hubble in GOODS-S and COSMOS. GZH doesn't

\begin{itemize}
\item AEGIS has 1 orbit each ($\sim2200$~seconds) in the F606W (V-band) and F814W (I-band) filters and has been dithered to 0.03~\arcsec/pixel; the imaging covers $\sim710$~arcmin$^2$.

\item GOODS targeted 2 fields, GOODS-N and GOODS-S, imaging in 4 filters -- F435W (B), F606W (V), F775W (i), and F850LP (z). The mean exposure times vary, from 1000 -- 2100~seconds. The images have been dithered to a pixel scale of 0.03~\arcsec/pixel and covers a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per field). The filters that \citet{gri12} uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.

\item COSMOS has 1 orbit (2028~seconds) in the F814W (I-band) filter and has been dithered to 0.05~\arcsec/pixel; it covers the largest area, $\sim1.8$~deg$^2$.

\item GEMS has 1 orbit (2160 and 2286~seconds in the F606W and F850LP filters, respectively) with a pixel scale of 0.03~\arcsec/pixel; it covers $\sim800$~arcmin$^2$
\end{itemize}

@@

\begin{table*}
\caption{Summary of Galaxy Zoo: Hubble imaging \label{gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                         & 2200        & F606W (V) and F814W (I)                     & 0.03 & 710   & 8157  \\
COSMOS                        & 2028        & F814W (I)                                   & 0.05 & 6480  & 88530 \\
GEMS                          & 2160$-$2286 & F606W (V) and F850LP (z)                    & 0.03 & 800   & 9143  \\
GOODS                         & 1000$-$2100 & F435W (B), F606W (V), F775W (i), F850LP (z) & 0.03 & 320   & 7336  \\
\hspace{10pt} \emph{GOODS-N}  & $-$         & $-$                                         & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S}  & $-$         & $-$                                         & $-$  & $-$   & \emph{4785}  \\
\hline
total                         & $-$         & $-$                                         & $-$  & 8310  & 113166  \\
\hline\hline
\end{tabular}
\end{table*}

@@

@@

\subsection{Selection of FERENGI Input Galaxies}

@@

\subsection{Morphological measurements in GZH beyond Task 1}

@@

@@

@@

This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \texttt{http://www.galaxyzoo.org/volunteers}. Galaxy Zoo 2 was developed with the help of a grant from The Leverhulme Trust.

We thank ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, Mar 3-7 2014 in Taipei, Taiwan, at which some of this analysis was done.

This project made heavy use of the Astropy packages in Python \citep{ast13}, as well as the seaborn plotting package \citep{was15}.

>>>>

% Bands

\newcommand{\Bband}{$B_{435W}$}
\newcommand{\Vband}{$V_{606W}$}
\newcommand{\iband}{$I_{775W}$}
\newcommand{\Iband}{$I_{814W}$}
\newcommand{\zband}{$I_{850LP}$}

@@

\textit{Usual due diligence for an intro science paper. Should cover:}

\begin{enumerate}
    \item Motivation for studying morphology of galaxies
    \item Particular scientific questions governed by galaxies at $z\sim1$
    \item Theoretical predictions for galaxy morphology evolution
    \item Past imaging and morphology studies at $z\sim1$
    \item Summary of GZ/citizen science work on galaxy morphology to date
\end{enumerate}

@@

\begin{itemize}
\item Hubble ACS imaging for the All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. The strip was originally selected due to low extinction and Galactic/zodiacal emission, making it a prime target for multi-wavelength observations by space-based observatories. The ACS images covered 63 separate tiles over a total area of $\sim710$~arcmin$^2$. Images were in two bands, with exposure times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband). The final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel. For extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in \Vband{} and 25.61 (AB) in \Iband.

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04} covers two well-studied fields in the northern and southern hemispheres: the Hubble Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m}, \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). Data including Hubble ACS images are referred to as GOODS-N and GOODS-S, respectively. ACS imaged the GOODS fields in 4 filters -- F435W (\Bband), \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each epoch vary by band, from 1050--2100~seconds. The \Bband{} images were completed in a single epoch at the beginning of the survey, but the \Vband, \iband, and \zband{} images were taken in five separate epochs separated by 40--50~days each. The ACS images are dithered to a pixel scale of 0.03~\arcsec/pixel and covers a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per field). The $5\sigma$ limiting magnitudes for extended sources are 25.7 for \Vband{} and 25.0 for \iband.

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m}28^\textrm{s}, \delta=+02^\circ12^\prime21^{\prime\prime}$. Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, as well as the space-based observatories. The Hubble ACS data from COSMOS consists of 1 orbit with 2028~seconds per pointing in \Iband, consisting of 590 total pointings. The image resolution is dithered to 0.05~\arcsec/pixel. The 50\% completeness magnitude for a galaxy with a half-light radius of $0^{\prime\prime}.50$ in \Iband{} is 24.7 mag.

\item The Galaxy Evolution from Morphologies and SEDS \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep Field-South. The GEMS data covers $\sim800$~arcmin$^2$, and surrounds the area covered by GOODS-S. Images from ACS in GEMS have 1 orbit per pointing for a total of 63~pointings. The exposure times are 2160 and 2286~seconds in \Vband{} and \zband{}, respectively. The image resolution has a pixel scale of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitudes for source detection are 25.7 AB in \Vband{} and 24.2~AB in \zband. 
\end{itemize}

@@

\begin{table*}
\caption{Summary of Galaxy Zoo: Hubble imaging \label{gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                         & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
COSMOS                        & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   & 7336  \\
\hspace{10pt} \emph{GOODS-N}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S}  & $-$         & $-$                              & $-$  & $-$   & \emph{4785}  \\
\hline
total                         & $-$         & $-$                              & $-$  & 8310  & 113166  \\
\hline\hline
\end{tabular}
\end{table*}

\subsection{Image creation}

The GOODS images in GZH use mosaics constructed from both 2-epoch and 5-epoch sets of data.

The filters that \citet{gri12} uses for the colored images were F606W and F775W for GOODS-N and F606W and F850LP for GOODS-S.

We use different filters for the north and south GOODS fields so that GEMS can be directly compared with GOODS-S.

Fake AGN

Stripe 82

Different treatment of colored noise in COSMOS; creating color gradients with Subaru data and using \Iband{} for illumination map.

FERENGI images.

@@

\section{Galaxy Zoo interface and classifications}

\begin{figure*}
\includegraphics[width=160mm]{figures/gzh_interface.png}
\caption{Screenshot of the Galaxy Zoo: Hubble interface showing an example COSMOS image at the first step in the decision tree.\label{fig:interface}}
\end{figure*}

@@

\subsection{Selection of FERENGI input galaxies}

@@

\subsection{Morphological measurements in GZH beyond Task 1 - effects of debiasing?}

@@

\subsection{Fake AGN}

@@

To include: detailed description of each column in the machine-readable tables.

Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2.

\section{Analysis}

\subsection{Demographics of morphology}

Summarize the broad trends that are seen regarding the fraction of galaxies with various morphologies, how that relates to color, size, etc. Briefly discuss results as compared with literature and theory.

\subsection{Comparison to other catalogs}

Compare GZH data to:

\begin{itemize}
    \item \citet[ZEST;][]{sca07} (COSMOS)
    \item Tasca (COSMOS)
    \item Cassata (COSMOS)
    \item Zajmoski (COSMOS)
    \item GEMS morphologies?
    \item AEGIS morphologies?
    \item GOODS N/S morphologies?
    \item expert visual inspection?
\end{itemize}

\textit{Address trends seen in broad morphological classes, possible reasons for difference. Also should attempt to map between the GZH vote fractions and whatever classification systems are used in the above systems.}

@@

This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \texttt{http://www.galaxyzoo.org/volunteers}.

We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this analysis was done.

This project made heavy use of the Astropy packages in Python \citep{ast13}, as well as the \texttt{seaborn} plotting package \citep{was15}.
